### 2020-01-27 ChapterImplementation/chapterImplementation.tex
Updated: More TODOs in Implementation and new subsection on Client-defined server regions

%TODO: Talk about edge-cases of multiple types of messages being sent in on tick.

@@

An object has two entry states, it is either received from another server via the network or it is injected into the simulation. Immediately the object's position determines its next state. If the object is not intersecting a server boundary and is not colliding with an aura, the object moves into the Host Region state. If the object is intersecting a sever boundary, it moves into the intersecting boundary state. If the object is outside of the server's region, such as is if the object is injected into a server at position the server is not responsible for, the object changes states to the boundary traversed state.
%TODO: Remaning states and transitions

@@

%TODO: Add client-created server regions feature

@@

>>>>

%TODO: Talk about messages arriving in and out of order. RakNet's ordered feature
%TODO: Talk about edge-cases of multiple types of messages being sent in on tick.

@@

An object has two entry states, it is either received from another server via the network or it is injected into the simulation. Immediately the object's position determines its next state. If the object is not intersecting a server boundary and is not colliding with an aura, the object moves into the Host Region state. If the object is intersecting a sever boundary, it moves into the intersecting boundary state. If the object is outside of the server's region, such as is if the object is injected into a server at position the server is not responsible for, the object changes states to the boundary traversed state.

%TODO: Host region to intersecting boundary or AC/Sent
%TODO: Intersecting Boundary to Host region, to Boundary Traversed, to AC/Sent
%TODO: Boundary Traversed, back to self (checking for islands) or Sent if island found or AC, to Intersecting Boundary
%TODO: Remaning states and transitions

@@

@@

\subsection{Client-defined server regions}
Through the editor at edit-time, it is possible to define the regions that each server should be responsible for. Using Unreal Engine's box colliders, a user can specify the area of each server region. Upon establishing connections with all servers, the client then communicates the area for each region with the servers through RPCs. In addition to this, servers are able to automatically calculate their neighbouring regions and establish appropriate communications with them; linking boundaries with corresponding servers and determining which servers to broadcast auras to.
